---
title: "eds-day-5Morning-session"
format: html
execute:
  warning: false
editor: visual
editor_options: 
  chunk_output_type: console
---

## Hi Amanda, its Rachel!

*Amanda Overbye*

```{r}

#| message: false
#load libraries
library(tidyverse)
```

'head()', 'tail()', and 'dim()', on the 'dplyr::starwars' data fram:

```{r}
#| include: false
# doing data exploration of db(starwars)
head(starwars)
tail(starwars)
dim(starwars)
```

Creat a ggplot (scatterplot) of character mass (y-axis) and height (x-axis) - update the color of the points so the color changes based on value of 'mass'

```{r}

#| echo: false
ggplot(data = starwars, aes(x = height, y = mass, color = mass)) +
       geom_point() +
       labs(title = "Starwars Character Mass Based On Height", 
            x = "Height(cm)",
            y = "Mass (kg)")

```

-   create a historgam of character heights
-   update the fill color ('fill') to purple and the outside boarder line ('color') of each histogram bin to orange
-   update your code chunk options so that only your code and output graph appear in the rendered doc (no warnings or messages)

```{r}
#| fig-cap: "caption text"
#| fig-alt: "figure alt text"
#| echo: false
ggplot(data = starwars, aes(x = height)) +
  geom_histogram(fill = "purple", color = "orange")+
  labs(title = "Starwars Height Chart,")
 
```

'df\$colname'

```{r}
sw_height_mean <- round(x = mean(starwars$height, na.rm = TRUE),digits = 3)

```

The mean height of all Starwars characters is `r sw_height_mean`

```{r}

```
